Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-13 paper/abstract.tex
Abstract Wordsmithing

Cyber-physical systems, such as avionics, must be tolerant to cyber-attacks in the same way they are tolerant to random faults: they either recover or safely shut down as requirements dictate. The DARPA Cyber Assured Systems Engineering program is developing design, analysis, and verification tools that enable systems engineers to design-in cyber-resiliency in a Model-Based Systems Engineering environment. This paper describes automated model transformations that introduce  high-assurance cyber-resiliency components into a system, in particular filters and monitors that prevent malicious input and detect supply chain attacks, respectively. A formal specification defines each component and is used to verify that the component addresses system level cyber requirements. Implementations are synthesized from the specifications, and that synthesis is proven to preserve the exact meaning of the specifications. The transformations are integrated into the Open Source AADL Tool Environment (OSATE). The paper further reports a case study applying these transformations to a UAV system that uses the Air Force Research Laboratory's OpenUxAS services for route planning. In the case study, the transforms add filters to guard against malformed input and monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS.

>>>>

Cyber-physical systems, such as avionics, must be tolerant to cyber-attacks in the same way they are tolerant to random faults: they either recover or safely shut down as requirements dictate. The DARPA Cyber Assured Systems Engineering program is developing design, analysis, and verification tools that enable systems engineers to design-in cyber-resiliency in a Model-Based Systems Engineering environment. This paper describes automated model transformations that introduce  high-assurance cyber-resiliency components into a system, in particular filters and monitors that prevent malicious input and detect supply chain attacks, respectively. A formal specification defines each component, and is used to verify that the component addresses system level cyber requirements. Implementations are directly synthesized from their specifications, and are automatically proven to preserve the exact meaning of the specifications all the way down to the binary code level. The model transformations are integrated into the Open Source AADL Tool Environment (OSATE). The paper further reports on a case study applying security-enhancing model transformations to a UAV system that uses the Air Force Research Laboratory's OpenUxAS services for route planning. In the case study, the model transformations add filters to guard against malformed input, as well as monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS.

### 2021-05-13 paper/paper.tex
Add formalism to AGREE semantics
Remove appendix
Abstract Wordsmithing

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
\and
\IEEEauthorblockN{
Isaac Amundson and
Konrad Slind}
\IEEEauthorblockA{
Trusted Systems Group   \\
Collins Aerospace       \\
Minneapolis, Minnesota}
\and
\IEEEauthorblockN{
Junaid Babar and 
David Hardin}
\IEEEauthorblockA{
Trusted Systems Group   \\
Collins Aerospace       \\
Cedar Rapids, Iowa}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\section{AGREE Specification}
\input{agree}

@@

\appendix
\section{Contiguity Types}
\input{contig}

\section{System Model and Semantics}
\input{system}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
\and
\IEEEauthorblockN{
Isaac Amundson and
Konrad Slind}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Minneapolis, Minnesota}
\and
\IEEEauthorblockN{
Junaid Babar and 
David Hardin}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Cedar Rapids, Iowa}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\section{AGREE Contract Specification}
\input{agree}

@@

% \appendix
% \section{Contiguity Types}
% \input{contig}

% \section{System Model and Semantics}
% \input{system}
